### 2017-11-02 manuscript.rmd
added cliffhanger at the end of the tentilla evolution section
Fixed bract evolution text

Bracts also present a complex evolutionary history of subtypes (Figure X). Bracts are highly reduced zooids unique to siphonophores, but they are only present in the Codonophora. As with the nectosome, we have ambiguity determining whether the MRCA of siphonophores had bracts or not. The MRCA of Codonophora ahd only one bract subtype, which was lost in Hippopodidae and independently evolved into 2 subtypes in *Erenna* and *Nanomia*. During the branch leading to Forskalidae, bract subtypes evolved from 1 to 4 morphologically distinct forms. Bracts are important for protection of the delicate zooids and to help maintain neutral buoyancy. Some calycophorans are able to actively regulate the Na/NH4 balance to adjust their buoyancy (ref).

@@

Palpons are modified mouthless gastrozooids used for digestion and circulation of the gastrovascular fluid. They were present in the MRCA of siphonophores (Figure X), retained in most species, but lost twice independently in the branches leading to *Bargmannia* and Calycophorae. These taxa must have found other avenues to effectively circulate nutrients across the colony.

@@

>>>>

Bracts are highly reduced zooids unique to siphonophores, but they are only present in the Codonophora. As with the nectosome, we have ambiguity determining whether the MRCA of siphonophores had bracts or not. The MRCA of Codonophora ahd only one bract subtype, which was lost in Hippopodidae and in *Gymnopraia lapislazula*. Bracts are important for protection of the delicate zooids and to help maintain neutral buoyancy. Some calycophorans are able to actively exclude suphate ions in their bracts to adjust their buoyancy along the colony Bidigare, R. R., & Biggs, D. C. (1980).

@@

Palpons are modified mouthless gastrozooids used for digestion and circulation of the gastrovascular fluid. They were present in the MRCA of siphonophores (Supp Figure X), retained in most species, but lost twice independently in the branches leading to *Bargmannia* and Calycophorae. These taxa must have found other avenues to effectively circulate nutrients across the colony.

@@

Siphonophore tentilla present an astounding diversity of sizes, shapes, colors, and nematocyst complements, and some have been observed to rapidly uncoil in contact with prey. Future research should explore the evolutionary history of these unique structures.
